Integrated nested Laplace approximations for extended latent Gaussian models with application to the Naomi HIV model

### 2022-12-21 src/docs_paper/paper.Rmd
Add naomi.cpp to appendix. Start writing main text model description

The remainder of this paper is organised as follows.
In Section \ref{sec:naomi} we describe the Naomi model.
Section \ref{sec:fastinferencemethods} outlines our approach to fast, accurate Bayesian inference using simplified INLA and AGHQ.
As a case-study, we fit the Naomi model on data from Malawi, and compare the accuracy of inferences in Section \ref{sec:naomi}.
In this section, we also demonstrating a Bayesian workflow.
Finally, in Section \ref{sec:conclusions} we discuss our conclusions, how our method might be used in other models, and directions for future research.

# The Naomi model\label{sec:naomi}

@eaton2021naomi specify a joint model linking small-area estimation models of HIV prevalence from household surveys, HIV prevalence from antenatal care clinics, and antiretroviral therapy (ART) coverage from routine health data collection.
Modelling data from multiple sources concurrently is attractive as it increases statistical power, mitigates the biases of any single source, and prompts investigation into any data conflicts.

In this work, we consider a modified version of the model, with temporal projection omitted.
In this section, we provide an overview of the model structure, with full details provided in the appendix.

@@

>>>>

The remainder of this paper is organised as follows.
In Section \ref{sec:naomi} we describe a modified version of the Naomi model that we consider.
Section \ref{sec:fastinferencemethods} outlines our approach to fast, accurate Bayesian inference using simplified INLA and AGHQ.
As a case-study, we fit the modified Naomi model on data from Malawi, and compare the accuracy of inferences in Section \ref{sec:naomi}.
In this section, we also demonstrating a Bayesian workflow.
Finally, in Section \ref{sec:conclusions} we discuss our conclusions, how our method might be used in other models, and directions for future research.

# A modified Naomi model\label{sec:naomi}

@eaton2021naomi specify a joint model linking small-area estimation models of HIV prevalence from household surveys, HIV prevalence from antenatal care clinics, and antiretroviral therapy (ART) coverage from routine health data collection.
Modelling data from multiple sources concurrently is beneficial as it mitigates the limitations of any single source, increases statistical power and prompts investigation into data conflicts.

For each country, the full model is defined over three time points: $T_1$, the time of the most recent household survey with HIV testing; $T_2$, the current time period; and $T_3$, a short term projection period.
We consider a simplified version of the full model which is defined only at $T_1$ and omits temporal projection.
In this section, we provide an overview of the modified model, highlighting the aspects which make it a challenge for existing inferential approaches.
Full mathematical details of this modified model, as well as a \textsf{C++} template for the log-posterior, are provided in the appendix.

@@

Let $i$ index the coarsest space-age-sex division included in the model.
Let $N_i$ be the population size and consider the following indicators: HIV prevalence $\rho_i$, annual HIV incidence rate $\lambda_i$ and ART coverage $\alpha_i$.
